The responses of \textit{\textit{Spinifex littoreus}} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China

### 2021-01-03 drafts/Response letter.md

January 3st, 2020

Editor-in-Chief
*Ecoscience*

Dear Dr. Hugo Asselin,

![Screenshot](https://gitee.com/SongshGeo/PicGo_picbed/raw/master/img/%E5%BE%AE%E4%BF%A1%E5%9B%BE%E7%89%87_20210103104911.png)

@@

We have followed all your suggestions in our revision. Below are the reviewer’s previous comments, followed by our responses.

Sincerely,
Shuang Song

---

***[Reviewer #1 Comment #1]*** The ms of Song et al concerns the adaptive capacity of psammophytes to sand burial as a crucial factor for the ecological restoration of coastal dune systems. The aim of the study was to analyze the responses of a typical for the coastal area of South China psammophytic species (Spinifex littoreus) to different sand burial depths and levels. The study is particularly relevant as coastal dunes in China are highly endangered (as many coastal dune systems in the world). The study is also very interesting and well conducted and reports valuable information, which could be a useful tool in the future for a natural and environmentally friendly way for protection and restoration of coastal dune systems in the area. In my opinion, the ms is worth to be published, just minor changes are requested.

***[Response]*** We are grateful to reviewer #1 for the effort reviewing our paper and his/her positive feedback. The information of our work as written by this reviewer is useful and critical. Here below we address the questions and suggestions raised by the reviewer #1.

***[Reviewer #1 Comment #2]*** Line 116: Figure 1. is the third Figure, mentioned in the text, so I think it would be better to renumber it to Figure 3. and renumber the other Figures accordingly.

***[Response]*** Since we re-analyzed our data, we have re-organized manuscript with figures where numbers are well renumbered.

***[Reviewer #1 Comment #3]*** Lines 117-119: Can you provide a reference, that concerns flora and/or vegetation of nebkhas/foredunes in the area?

***[Response]*** We added some new cites in the proper position of ms now (e. g. (Yang et al. 2017, Divyasree & Raju 2019)) to describe the vegetation in this area.

***[Reviewer #1 Comment #4]*** Line 125: How did you compare the age of different plants?

***[Response]*** Thanks for pointing this out. In fact, we only compare them by size (we mis-wrote in the last version.).

***[Reviewer #1 Comment #5]*** Lines 127-129: Did you measure the height of vertical ramets and the length of stolons to know they were all similar with each other before choosing the plants for the study?

***[Response]*** Yes, we started our measurements in the first day of experiment and we show them in the figures now [**see Figure 5**].

***[Reviewer #1 Comment #6]*** Line 131: What do you mean by "weeds" - all plant species around the selected plants, or particular species, that you consider undesirable, which tend to overgrow or choke out more desirable plants?

***[Response]*** Thanks for the valuable comment, this has been clarified in the revised version of the manuscript:

> **[Line 130-131]** All plant species around the selected plants were manually cleared, and...

***[Reviewer #1 Comment #7]*** Lines 269-272: This sentence is not clear to me.

***[Response]*** Thanks for pointing this out, we have deleted this unclear sentence.

***[Reviewer #1 Comment #8]*** Although I'm not a native English speaker, I believe that English should be improved. I wouldn't say it is poor but it needs to be revised. Some examples:
Lines 28-29: Sand dunes occupy a finite area in coastal regions, but they are characterized by providing multiple ecological services, …
Line 57: The tolerance capacity to different sand burial levels is varied among species, …
Lines 142-143: Since the height of vertical ramets of S. littoreus is relatively high, it is usually impossible for them to be completely buried in the sand.

***[Response]*** Thanks for the valuable comment, this has been clarified in the revised version of the manuscript.

@@

***[Response]*** Thank you for acknowledging the importance of our research and we have now restructured the manuscript so that these important questions can be clearly answered and discussed in a focused manner.

**Introduction:**

***[Reviewer #2 Comment #2]*** I think the introduction is well done. The authors include adequate information and have clearly shows their understanding of the dune burial literature. Primarily I think the introduction would benefit from a clear hypothesis statement. The objectives of the project are clear, but I think the reader will benefit from a hypothesis which will orient the reader so that they know what the experts (the authors) are expecting from their study.

***[Response]*** Thanks to your positive comments and useful suggestions, we now clearly give our scientific hypothesis:

> **[P3: L94-96]** In this study, we assume that the growths of *S. littoreus* can be facilitated with the increase of sand burial, which is probably the key factor for this native plant to adapt to the intense sand burial caused by frequent typhoon events in growing seasons.

@@

Some other line by line comments:

***[Reviewer #2 Comment #3]*** Line 63-67 - These two sentences present similar results, but the author makes it seem as though they are contradictory – consider revising.

***[Response]*** Thank you for pointing this out, we have now changed them to a paratactic relationship **[P2, L63-67]**:

> [P2, L63-67] Wang (2005) demonstrated that both stem height in the vertical direction and leaf weight of Messerschmidia sibirica were increased with light sand burial, while they all decreased with moderate treatments contrasted with the control. In addition, Zhou et al. (2015a) showed that the growth of Artemisia desterorum was enhanced with moderate sand burial, but inhibited with intense sand burial.

***[Reviewer #2 Comment #4]*** Line 83 – the term nebkhas is a little jargony - readers that are not familiar with types of dunes will not know what this is. I suggest defining more clearly.

**[Response]** Thank you for pointing this out, we now give a simple note **[P2, L82-83]**:

@@

***[Reviewer #2 Comment #12]*** There are a lot of results for this paper and I think some for the most important results get lost in the complexity of the results section as a whole. I think this paper will benefit from pairing down the results to the most important results that contribute most to the gaps in dune grass burial literature.

***[Response]*** Thank you for your valuable suggestions, we have now significantly streamlined the results and focused on two main points:

- Inﬂuence of sand burial on the growths of S. littoreus
- Inﬂuence of sand burial on the biomass allocation of S. littoreus

***[Reviewer #2 Comment #13]*** Specific comments in the results section:
Line 213-216 – This section again appears to be results of a two-way ANOVA in which the author is analyzing how burial is impacted by burial based on time period - however, the statistical analysis section does not talk about the author running a factorial ANOVA.

***[Response]*** We have rewritten the results section and now ensure that both the charts and the text show the interaction issues of time correctly in **[Figure 4]**.

***[Reviewer #2 Comment #14]*** Line 223 – Delete “In half sand burial”

***[Response]*** Thanks for this specific useful comment, rectified.

***[Reviewer #2 Comment #15]*** Line 237-240 – This seems a little unclear. It is unclear how important some of these results are to the study. I think this clarity could be improved by incorporating a hypothesis in the introduction.

***[Response]*** We have re-analysed the data and show the results of the biomass allocation in a dedicated section **[see section result Inﬂuence of sand burial on the biomass allocation of S. littoreus]**.

### 2021-04-28 tex/interactcsesample.tex
Article published

\documentclass[]{interact}
\usepackage{lineno}
\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required

@@

\author{
\name{
  Shuang Song\textsuperscript{a}, 
  Jianhui Du \textsuperscript{a,b} \thanks{CONTACT Jianhui Du. Email: dujh1982@hotmail.com}, 
  Qirui Wu \textsuperscript{a},
  Mingyang Ni \textsuperscript{a}, Yijia Wang \textsuperscript{a} and Yingling Zhang \textsuperscript{a}}\affil{\textsuperscript{a}School of Geography and Planning, Sun Yat-Sen University, Guangzhou, 510275, China; \textsuperscript{b} Guangdong Key Laboratory for Urbanization and Geo-simulation, Guangzhou, 510275, China}
}

>>>>

\documentclass[]{interact}
\usepackage[lists]{endfloat}
\usepackage{lineno}
\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required

@@

\author{
\name{
  Shuang Song\textsuperscript{a,b,c}, 
  Jianhui Du \textsuperscript{a,d} \thanks{CONTACT Jianhui Du. Email: dujh1982@hotmail.com}, 
  Qirui Wu \textsuperscript{a},
  Mingyang Ni \textsuperscript{a}, Yijia Wang \textsuperscript{a,b,c} and Yingling Zhang \textsuperscript{a}}\affil{\textsuperscript{a}School of Geography and Planning, Sun Yat-Sen University, Guangzhou, 510275, China; \textsuperscript{b} State Key Laboratory of Earth Surface Processes and Resource Ecology, Faculty of Geographical Science, Beijing Normal University, Beijing 100875, China; \textsuperscript{c} Institute of Land Surface System and Sustainability, Faculty of Geographical Science, Beijing Normal University, Beijing 100875, China;\textsuperscript{d} Guangdong Key Laboratory for Urbanization and Geo-simulation, Guangzhou, 510275, China}
}
